14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-15 rules/rules19.tex
Minor edits to industry challenge track.

\todo{time limit}
The \challenge Track will follow the same rules as the \main Track,
with two exceptions: benchmark selection and the time limit. The track will run on benchmarks nominated by the community.
\lh{TODO: benchmark selection still needs discussion}
\lh{TODO: scored in the same way as main track (mention later not here)}

>>>>

\todo{time limit}
The \challenge Track will include both incremental and single query benchmarks and it will follow the same rules as the \incremental and  \main Track, respectively with two exceptions: benchmark selection and the time limit. The track will run on challenging industrial benchmarks provided by the community.
